DNA meth and IVF

### 2023-12-19 figs/art_example.Rmd
fix art example

det <- mres$detailed_sets$REACTOME_SENSORY_PERCEPTION

@@

filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome sensory perception", xlab = X_AXIS,
        ylab = Y_AXIS)
    })

pdf("fig7d.pdf")
filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome sensory perception", xlab = X_AXIS,
        ylab = Y_AXIS)
    })
dev.off()

>>>>

tic()
mres <- mitch_calc(x=m,genesets=gs_symbols,minsetsize=5,cores=16, priority="significance")
toc() #11.45s

det <- mres$detailed_sets$REACTOME_NUCLEAR_EVENTS_KINASE_AND_TRANSCRIPTION_FACTOR_ACTIVATION

@@

filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome nuclear kinase and transcription factor activation", xlab = X_AXIS,
        ylab = Y_AXIS)
    })

pdf("fig7d.pdf")
filled.contour(k, color.palette = palette, xlim=c(XMIN,XMAX), ylim=c(YMIN,YMAX),
      plot.title = {
        abline(v = 0, h = 0, lty = 2, lwd = 2, col = "blue")
        title(main = "Reactome nuclear kinase and transcription factor activation", xlab = X_AXIS,
        ylab = Y_AXIS)
    })
dev.off()

det <- cbind(det, apply(det,1,median))

det <- det[order(det[,3]),]

head(det,20) %>% kbl(caption="Top hypomethylated genes of the selectedpathway") %>% kable_paper("hover", full_width = F)
